\pdfminorversion=4
\documentclass{letter}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{xcolor,url}

\signature{Valéria S. Girelli\\Francis B. Moreira\\Matheus S. Serpa\\Danilo Carastan-Santos\\Philippe O. A. Navaux}
\address{Informatics Institute\\Federal University of Rio Grande do Sul\\Porto Alegre, Brazil}

\widowpenalty=10000
\clubpenalty=10000

\begin{document}



\begin{letter}{}


\opening{Dear Editor-in-Chief:}


Regarding the similarity report, which indicates a 3\% similarity with \emph{http://users.elis.ugent.be/}. In Section 2.2.2 of the paper, we made corrections to the citations, in order to properly cite the following papers: 
\begin{itemize}
    %ref 13
    \item Eyerman, S., Eeckhout, L., Karkhanis, T., \& Smith, J. E. (2009). A mechanistic performance model for superscalar out-of-order processors. ACM Transactions on Computer Systems (TOCS), 27(2), 1-37.
     
    %ref 6
    \item Carlson, T. E., Heirman, W., Eyerman, S., Hur, I., \& Eeckhout, L. (2014). An evaluation of high-level mechanistic core models. ACM Transactions on Architecture and Code Optimization (TACO), 11(3), 1-25.
    
    %ref 12
    \item Genbrugge, D., Eyerman, S., \& Eeckhout, L. (2009). Raising the level of abstraction in architectural simulation. In 9th ACES Symposium (ACES'09) (pp. 49-52).
\end{itemize}
 
%We also rewrite/paraphrase the similar parts ... TODO TODO as follows:

%\begin{itemize}
%	\item a
%	\item b
%	\item c
%\end{itemize}

We look forward to hearing from you about this issue at your earliest convenience.

\closing{Sincerely,}

\end{letter}

\end{document}


